Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2012-09-15 chi2012.tex
some edits to intro

Third, we developed DataPalette, which focuses on the most common types of heterogeneity to enable serendipitous ``data mixing'' - a form of simple integration sufficient to allow people to easily and effectively combine and compare information sources without the need to write code.  It was principally designed based upon people's data integration needs and to support data heterogeneity observed in the previous studies.  We embarked on a user-centric design exercise towards an interface to facilitate simple, ``light-touch'' integration tasks of diverse, heterogeneous data sources.  We then performed a usability evaluation of DataPalette, which revealed that most users were comfortable with and that this interface is effectively expedites the most sophisticated of the typical kinds of ``data integration'' tasks people need to perform while planning personal.

>>>>

Third, we developed DataPalette, which focuses on the most common types of heterogeneity to enable serendipitous ``data mixing'' - a form of simple integration sufficient to allow people to easily and effectively combine and compare information sources without the need to write code.  It was principally designed based upon people's data integration needs and to support data heterogeneity observed in the previous studies.  We embarked on a user-centric design exercise towards an interface to facilitate simple, ``light-touch'' integration tasks of diverse, heterogeneous data sources.  We then performed a usability evaluation of DataPalette, which revealed that most users were comfortable with the interactive integration mechanisms we devised, and that this interface effectively improved people's ability to perform multifaceted decision making tasks using multiple sources.
